Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake

### 2016-07-07 JGRRevision/2016JB013114.tex
a few more edits

The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.  The largest misfit occur within the Imperial Valley and there does not appear to be any systematic trend in the residuals.  This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.  We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.  We do notice regionally uniform seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.  This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.  Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation following those earthquakes.  Lastly, there are clear discrepancies between the observed and predicted vertical displacements following the first year after the El Mayor-Cucapah earthquake. We observe a broad uplift throughout Southern California which is inconsistent with any postseismic model.

@@

\section*{Acknowledgements}
We thank Andy Freed for an illuminating discussion on the data used in this study.  We also thank F. Pollitz and an anonymous reviewer for comments that improved this manuscript, and Editor Martha Savage.  This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No. EAR-1261833.  The data used in this study can be found at www.unavco.org. This material is based upon work supported by the National Science Foundation under Grant Numbers EAR 1045372 and EAR 1245263.

>>>>

The postseismic displacements predicted by our preferred Zener model are shown in Figures \ref{fig:NearField}, \ref{fig:FarField} and \ref{fig:RecordSectionMain}.  The largest misfit occur within the Imperial Valley and there does not appear to be any systematic trend in the residuals.  This suggests that the large errors are due to localized processes such as fault slip in the Imperial Valley triggered by the El Mayor-Cucapah earthquake \citep{Wei2011a,Wei2015}.  We do not see any pattern in the residuals that would suggest a laterally heterogeneous viscosity structure, which has been explored by \citet{Pollitz2012} and \citet{Rollins2015}.  We do notice regional scale seasonal oscillations in the lateral and vertical components of the residuals with an amplitude of 1-2 millimeters.  This is the result of our method for data processing which is not able to completely remove the seasonal signal in the GPS data, which was discussed in Section \ref{sec:Data}.  Additionally, we see systematic misfit in the later postseismic period west of the Landers and Hector Mine earthquakes, which may be the result of unmodeled postseismic deformation following those earthquakes.  Lastly, there are clear discrepancies between the observed and predicted vertical displacements following the first year after the El Mayor-Cucapah earthquake. We observe a broad uplift throughout Southern California which is inconsistent with any postseismic model.

@@

\section*{Acknowledgements}
We thank Andy Freed for an illuminating discussion on the data used in this study.  We thank Fred Pollitz and an anonymous reviewer for comments that improved this manuscript. We also thank the editor, Martha Savage.  This material is based on EarthScope Plate Boundary Observatory data services provided by UNAVCO through the GAGE Facility with support from the National Science Foundation (NSF) and National Aeronautics and Space Administration (NASA) under NSF Cooperative Agreement No. EAR-1261833.  The data used in this study can be found at www.unavco.org. This material is based upon work supported by the National Science Foundation under Grant Numbers EAR 1045372 and EAR 1245263.
